A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2022-01-06 analysis/paper/paper.Rmd
Re-running analyses

The shore-bound settlement location of prehistoric hunter-fisher-gatherers in Norway is generally believed to follow both from a resource perspective and from one of movement and communication, which would have been efficient on waterways. The same logic has also been extended to the hinter- and inland regions, where sites are to be located along rivers and lakes. This general picture is to take a dramatic turn at the transition to the Late Neolithic, around 2400 BCE, where the introduction of the Neolithic proper inolved a. associated involving a change agro-pastoralism, the farm,  means that the site locations are now more withdrawn from the shoreline [@solheim2018; @prescott2012]. That is not to say that waterways and aquatic resources were no longer exploited, but rather that these activities would not have been as tightly integrated with settlement and tool-production areas as in preceding periods.

>>>>

The shore-bound settlement location of prehistoric hunter-fisher-gatherers in Norway is generally believed to follow both from a resource perspective and from one of movement and communication, which would have been efficient on waterways. The same logic has also been extended to the hinter- and inland regions, where sites are to be located along rivers and lakes. At the transition to the Early Neolithic there is an initial uptake of agriculture This general picture is to take a dramatic turn at the transition to the Late Neolithic, around 2400 BCE, where the introduction of the Neolithic proper inolved a. associated involving a change agro-pastoralism, the farm,  means that the site locations are now more withdrawn from the shoreline [@solheim2018; @prescott2012]. That is not to say that waterways and aquatic resources were no longer exploited, but rather that these activities would not have been as tightly integrated with settlement and tool-production areas as in preceding periods.
